Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey

### 2021-10-28 code/analysis_code/exploratory.Rmd
more exploratory analysis + manuscript update

@@

```
#people over 40
```{r}
data1 %>% 
     dplyr::filter(Age > 40 ) %>%
     group_by(Age) %>%
     summarise( percent = 100 * n() / nrow( data1) )

```

#percentage of male and female
```{r}
data1 %>% 
     group_by( Sex ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#number of people for each educational category
```{r}
table(data1$`education`)
```
```{r}
sum(data1$'education' == 'Primary')
sum(data1$'education' == 'Secondary')
sum(data1$'education' == 'University Postgraduate degree holder')
sum(data1$'education' == 'University Undergraduate degree holder')
```
#percentage of people for each student category
```{r}
data1 %>% 
     group_by( `education` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#student/worker in the heathcare sector?
```{r}
table(data1$`student/heathworker`)
```

@@

#percentage of income category?
```{r}
data1 %>% 
     group_by( `economic_status` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
```{r}
table(data1$`residence`)
```
```{r}
sum(data1$'residence' == 'A rural place / village')
sum(data1$'residence' == 'A Sub-urban setting / urban slum')
sum(data1$'residence' == 'An urban setting / city / town')
```
#percentage of living setup?
```{r}
data1 %>% 
     group_by( `residence` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`trusted_source`)
```
#most trusted source?
```{r}
data1 %>% 
     group_by( `trusted_source` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

@@

#percentage of work from home or not?
```{r}
data1 %>% 
     group_by( `work_from_home` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```
#Descriptive analysis for each question?
```{r}
table(data1$`quarantined_or_not`)
```
#Quarantined or not
```{r}
data1 %>% 
     group_by( `quarantined_or_not` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`infection_status_info`)
```
#correct knowledge of their status
```{r}
data1 %>% 
     group_by( `infection_status_info` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`worry_level`)
```
#worried about re-infection
```{r}
data1 %>% 
     group_by( `worry_level` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Heart disease`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Hypertension`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Diabetes`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Cancer`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): HIV`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Tuberculosis`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Asthma`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`)
```
```{r}
data1 %>% 
     group_by( `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
```

>>>>

#check if certain column is factor or not
```{r}
is.factor(data1$Sex)
```

@@

```
#people below 35
```{r}
age_summary = data1 %>% 
     dplyr::filter(Age < 36 ) %>%
     group_by(Age) %>%
     summarise( percent = 100 * n() / nrow( data1) )
print(age_summary)
```

```{r}
df1 = data.frame(age_summary)
summarytable_file = here("results", "summarytable.rds")
saveRDS(df1, file = summarytable_file)
```
#percentage of male and female
```{r}
sex_summary =data1 %>% 
     group_by( Sex ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(sex_summary)
```
```{r}
df2 = data.frame(sex_summary)
summarytable_file = here("results", "summarytable2.rds")
saveRDS(df2, file = summarytable_file)
```

#number of people for each educational category
```{r}
table(data1$`education`)
```
```{r}
sum(data1$'education' == 'Primary')
sum(data1$'education' == 'Secondary')
sum(data1$'education' == 'University Postgraduate degree holder')
sum(data1$'education' == 'University Undergraduate degree holder')
```
#percentage of people for each student category
```{r}
education_summary = data1 %>% 
     group_by( `education` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(education_summary)
```

```{r}
df3 = data.frame(education_summary)
summarytable_file = here("results", "summarytable3.rds")
saveRDS(df3, file = summarytable_file)
```

#student/worker in the heathcare sector?
```{r}
table(data1$`student/heathworker`)
```

@@

#percentage of income category?
```{r}
income_summary = data1 %>% 
     group_by( `economic_status` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(income_summary)
```
```{r}
df4 = data.frame(income_summary)
summarytable_file = here("results", "summarytable4.rds")
saveRDS(df4, file = summarytable_file)
```

```{r}
table(data1$`residence`)
```
```{r}
sum(data1$'residence' == 'A rural place / village')
sum(data1$'residence' == 'A Sub-urban setting / urban slum')
sum(data1$'residence' == 'An urban setting / city / town')
```
#percentage of living setup?
```{r}
residence_summary = data1 %>% 
     group_by( `residence` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(residence_summary)
```
```{r}
df5 = data.frame(residence_summary)
summarytable_file = here("results", "summarytable5.rds")
saveRDS(df5, file = summarytable_file)
```

```{r}
table(data1$`trusted_source`)
```
#most trusted source?
```{r}
source_summary = data1 %>% 
     group_by( `trusted_source` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(source_summary)
```
```{r}
df6 = data.frame(source_summary)
summarytable_file = here("results", "summarytable6.rds")
saveRDS(df6, file = summarytable_file)
```

@@

#percentage of work from home or not?
```{r}
work_From_home_or_not_Summary = data1 %>% 
     group_by( `work_from_home` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(work_From_home_or_not_Summary)
```
```{r}
df7 = data.frame(work_From_home_or_not_Summary)
summarytable_file = here("results", "summarytable7.rds")
saveRDS(df7, file = summarytable_file)
```

#Descriptive analysis for each question?
```{r}
table(data1$`quarantined_or_not`)
```
#Quarantined or not
```{r}
q_or_not_summary = data1 %>% 
     group_by( `quarantined_or_not` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(q_or_not_summary)
```
```{r}
df8 = data.frame(q_or_not_summary)
summarytable_file = here("results", "summarytable8.rds")
saveRDS(df8, file = summarytable_file)
```

```{r}
table(data1$`infection_status_info`)
```
#correct knowledge of their status
```{r}
test_status_summary = data1 %>% 
     group_by( `infection_status_info` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(test_status_summary)
```
```{r}
df9 = data.frame(test_status_summary)
summarytable_file = here("results", "summarytable9.rds")
saveRDS(df9, file = summarytable_file)
```
#worried about re-infection
```{r}
worry_level_summary = data1 %>% 
     group_by( `worry_level` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(worry_level_summary)
```
```{r}
df10 = data.frame(worry_level_summary)
summarytable_file = here("results", "summarytable10.rds")
saveRDS(df10, file = summarytable_file)
```

```{r}
table(data1$`worry_level`)
```

```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Heart disease`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Hypertension`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Diabetes`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Cancer`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): HIV`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Tuberculosis`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): Asthma`)
```
```{r}
table(data1$`Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above`)
```
```{r}
chronic_disease_history = data1 %>% 
     group_by( `Do you have any of the following chronic/underlying diseases? (many answers possible): None of the above` ) %>% 
     summarise( percent = 100 * n() / nrow( data1) )
print(chronic_disease_history)
```

```{r}
df11 = data.frame(chronic_disease_history)
summarytable_file = here("results", "summarytable11.rds")
saveRDS(df11, file = summarytable_file)
```

### 2021-10-28 products/manuscript/Manuscript.Rmd
more exploratory analysis + manuscript update

---
title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in nine low-and middle-income countries: an online survey"
subtitle: ""
author: Ehsan Suez
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

@@

_Enabling/disabling factors_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.

_Disabling factors_ include the assessment of psychological distress with the Patient Health Questionnaire (PHQ-4) for Depression and Anxiety symptoms [Kroenke/ Löwe]. The severity of psychological distress is categorized as normal (0-2), mild (3-5). moderate (6-8) and severe (9-12) based on the PHQ-4 scores.

@@

## Data import and cleaning_ [Here I mostly covered descriptive analysis]
---
title: "try"
author: "Ehsan"
date: "10/6/2021"
output: html_document
---

## Exploratory analysis

@@

@@

Table \@ref(tab:summarytable) shows a table summarizing the data.

>>>>

---
title: "Using Andersen’s model of health care utilization to assess factors associated with COVID-19 testing among adults in Bangladesh: an online survey"
subtitle: ""
author: Ehsan Suez
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
documentclass: article
output:
  bookdown::word_document2: 
    toc: false
    number_sections: true
  bookdown::html_document2: 
    toc: false
bibliography: ../references.bib
csl: ../apa.csl
---

@@

_Enabling/d_
Enabling factors include self-perceived socio-economic status, self-perceived area of residence, being a student or worker in the health care sector, source of COVID-19 information/advice most trusted (coded as other, including family and friends, radio/TV, social media, religious authorities and health personnel.

@@

## Data import and cleaning_ html_document
---
```{r}
library(here)
```
## Exploratory analysis

@@

```{r summarytable,  echo=FALSE}
resulttable=readRDS("../../results/summarytable.rds")
knitr::kable(resulttable, caption = 'Age Percentage of Participants.')
```
78.9% of total participants are less than or equal  to 35 years old.

```{r summarytable2,  echo=FALSE}
resulttable=readRDS("../../results/summarytable2.rds")
knitr::kable(resulttable, caption = 'Sex Percentage of Participants.')
```

```{r summarytable3,  echo=FALSE}
resulttable=readRDS("../../results/summarytable3.rds")
knitr::kable(resulttable, caption = 'Education Background Percentage of Participants.')
```

```{r summarytable4,  echo=FALSE}
resulttable=readRDS("../../results/summarytable4.rds")
knitr::kable(resulttable, caption = 'Income Percentage of Participants.')
```

```{r summarytable5,  echo=FALSE}
resulttable=readRDS("../../results/summarytable5.rds")
knitr::kable(resulttable, caption = 'Residence Percentage of Participants.')
```

```{r summarytable6,  echo=FALSE}
resulttable=readRDS("../../results/summarytable6.rds")
knitr::kable(resulttable, caption = 'Source of information Percentage of Participants.')
```

```{r summarytable7,  echo=FALSE}
resulttable=readRDS("../../results/summarytable7.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants working from home or not.')
```

```{r summarytable8,  echo=FALSE}
resulttable=readRDS("../../results/summarytable8.rds")
knitr::kable(resulttable, caption = 'Percentage of Participants quarantined or not at some stage.')
```

```{r summarytable9,  echo=FALSE}
resulttable=readRDS("../../results/summarytable9.rds")
knitr::kable(resulttable, caption = 'Percentage of covid test status of the participants.')
```

```{r summarytable10,  echo=FALSE}
resulttable=readRDS("../../results/summarytable10.rds")
knitr::kable(resulttable, caption = "Percentage of participants' worry level about (re)infection with COVID-19.")
```

```{r summarytable11,  echo=FALSE}
resulttable=readRDS("../../results/summarytable11.rds")
knitr::kable(resulttable, caption = "Percentage of participants' history of chronic disease")
```

@@
